---
Title: "Infants rationally decide when and how to deploy effort - Analyses"
Authors: "Kelsey Lucca, Rachel O. Horton, Jessica A. Sommerville"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, warning = FALSE,
                      tidy = TRUE)
```

```{r libraries}
#Load libraries
library(tidyverse)
library(lme4)
library(nlme)
library(lmtest)
library(lmerTest)
library(lsr)
library(afex)
```

```{r general-settings}

#define gray color palette & set base font size
cbbPalette <- c("grey77", "grey54", "grey28")
theme_set(theme_bw(base_size = 20))
```


```{r prepare-data}
#Prepare data for analysis

#Read in data file
BG <- read.csv("https://raw.githubusercontent.com/klucca/Lucca_et_al_Effort_2019/master/BG.csv")

#Set data types
as.factor(BG$TrialNumber_AsFactor)->BG$TrialNumber_AsFactor

#Dummy code variables for cross-condition comparisons
BG$Condition <- factor(BG$Condition, levels=c("Easy","Hard", "Impossible")) #Easy is baseline
BG$Condition_HardBase <- factor(BG$Condition_HardBase, levels=c("Hard","Easy", "Impossible")) #Hard is baseline
BG$Condition_ImpossibleBase <- factor(BG$Condition_ImpossibleBase, levels=c("Impossible","Hard", "Easy")) #Impossible is baseline


#Create additional dataframes for analysis

# Subset of data to get one row per individual in trial 1
BG %>% filter(TrialNumber=="1")-> BG_Trial1


# Subset time trying data to calculate effect sizes
timetrying_subset <- BG %>% select(SubjNum,TrialNumber,TimeTrying_sqrt,Condition)
timetrying_wide <- spread(data = timetrying_subset, key = TrialNumber, value = TimeTrying_sqrt) 
timetrying_wide<- rename(timetrying_wide, "one" = "1")
timetrying_wide<- rename(timetrying_wide, "two" = "2")
timetrying_wide<- rename(timetrying_wide, "three" = "3")
timetrying_wide_easy <- subset(timetrying_wide, Condition=="Easy")
timetrying_wide_hard <- subset(timetrying_wide, Condition=="Hard")
timetrying_wide_impossible <- subset(timetrying_wide, Condition=="Impossible")

```


######################################################
#   Section 1 Time Trying Analyses   #
###################################################### 

Figure 2. Infants’ trying behavior, time spent engaging with task,  
across conditions and trials. (left, n = 288 trials)  

```{r Time-Trying-plot, echo = FALSE}
#data viz in boxplot
ggplot(BG, mapping = aes(x = TrialNumber_AsFactor, y =  TimeTrying, fill=TrialNumber_AsFactor))+
  geom_boxplot(alpha=.6,outlier.shape = NA) + geom_jitter(alpha=.2,width=.1)+
  scale_fill_manual(values=cbbPalette)+ylab("Time spent trying (s)") + xlab("Trial Number")+
  facet_wrap(~Condition) +theme_bw()+ theme(legend.position="None")+
  theme(strip.text = element_text(size = 15)) + theme(axis.text.x =element_text(size = 15))+
  theme(axis.text.y =element_text(size = 15)) + theme(axis.title.y =element_text(size = 15))+
  theme(axis.title.x =element_text(size = 15))
```


```{r time-trying-table, results = 'asis', echo = FALSE}
#descriptive stats time trying
MeanTryingTime <- BG%>%
  filter(!is.na(TimeTrying)) %>%
  group_by(Condition,TrialNumber)%>%
  summarise(n=n(),
            mean_tryingtime = mean(TimeTrying,na.rm=TRUE),
            sd = sd(TimeTrying,na.rm=TRUE),
            se = sd/sqrt(n))
 knitr::kable(MeanTryingTime)
```

Time trying linear mixed effect model
```{r time-trying-analysis-part1}
#analyze time trying data, generate 95% CI, and run model comparisons, with easy as baseline
lmer(TimeTrying_sqrt~TrialNumber*Condition+(1|SubjNum),data=BG)->m1
summary(m1)
confint(m1)
lmer(TimeTrying_sqrt~(1|SubjNum),data=BG)->m0
anova(m0,m1)

#analyze time trying data with hard as baseline, generate 95% CI
lmer(TimeTrying_sqrt~TrialNumber*Condition_HardBase+(1|SubjNum),data=BG)->m1
summary(m1)
confint(m1)
lmer(TimeTrying_sqrt~(1|SubjNum),data=BG)->m0
anova(m0,m1)
```


Linear mixed effect model within conditions for time trying  
analyzing effect of trial number within each condition
```{r time-trying-analysis-part2}

#impossible condition linear mixed effect model for time trying
lmer(TimeTrying_sqrt~TrialNumber+(1|SubjNum),
     data=BG[BG[,"Condition"]=="Impossible",])->TimeTryingImpossibleCondModel
summary(TimeTryingImpossibleCondModel)
confint(TimeTryingImpossibleCondModel)

#easy condition linear mixed effect model for time trying
lmer(TimeTrying_sqrt~TrialNumber+(1|SubjNum),
     data=BG[BG[,"Condition"]=="Easy",])->TimeTryingEasyCondModel
summary(TimeTryingEasyCondModel)
confint(TimeTryingEasyCondModel)

#hard condition linear mixed effect model for time trying
lmer(TimeTrying_sqrt~TrialNumber+(1|SubjNum),
     data=BG[BG[,"Condition"]=="Hard",])->TimeTryingHardCondModel
summary(TimeTryingHardCondModel)
confint(TimeTryingHardCondModel)


cohensD(timetrying_wide_easy$one, timetrying_wide_easy$three,method="paired")
cohensD(timetrying_wide_impossible$one, timetrying_wide_impossible$three,method="paired")
cohensD(timetrying_wide_hard$one, timetrying_wide_hard$three,method="paired")
```


######################################################
#   Section 2 Force Analyses   #
###################################################### 
Figure 2. Infants’ trying behavior, maximum pulling force on the rope in pounds  
per square inch, across conditions and trials(center, n = 213 trials).  

```{r force-plot, echo = FALSE}
#data viz in boxplot
ggplot(BG, mapping = aes(x = TrialNumber_AsFactor, y =  MaxPSI,fill=TrialNumber_AsFactor))+
  geom_boxplot(alpha=.6,outlier.shape = NA)+ geom_jitter(alpha=.2,width=.1)+
  scale_fill_manual(values=cbbPalette)+ylab("Average Max Trying Force (psi)")+
  xlab("Trial Number")+facet_wrap(~Condition) +theme_bw()+ theme(legend.position="None")+
  theme(strip.text = element_text(size = 15))+theme(axis.text.x =element_text(size = 15))+
  theme(axis.text.y =element_text(size = 15))+theme(axis.title.y =element_text(size = 15))+
  theme(axis.title.x =element_text(size = 15))
```

```{r force-table, results = 'asis', echo = FALSE}
#descriptive stats max lb
MeanMaxLb  <- BG%>%
  group_by(Condition,TrialNumber)%>%
  filter(!is.na(MaxPSI)) %>%
  summarise(n=n(),
            mean_max_lb = mean(MaxPSI,na.rm=TRUE),
            sd = sd(MaxPSI,na.rm=TRUE),
            se = sd/sqrt(n))

 knitr::kable(MeanMaxLb)
```

Pulling force linear mixed effect model  
```{r force-analysis-part1}
#analyze max lb, compute CIs, and compare reduced and full models
lmer(MaxPSI_sqrt~TrialNumber*Condition+(1|SubjNum),data=BG)->MaxLbModel
summary(MaxLbModel)
confint(MaxLbModel)
lmer(MaxPSI_sqrt~(1|SubjNum),data=BG)->m0
anova(m0,MaxLbModel)
```

Linear mixed effect models within conditions for pulling force  
analyzing effect of trial number within each condition
```{r force-analysis-part2}

#Impossible condition linear mixed model for pulling force
lmer(MaxPSI_sqrt~TrialNumber+(1|SubjNum),
     data=BG[BG[,"Condition"]=="Impossible",])->ImpossibleMaxLbModel
summary(ImpossibleMaxLbModel)
confint(ImpossibleMaxLbModel)

#Easy condition linear mixed model for pulling force
lmer(MaxPSI_sqrt~TrialNumber+(1|SubjNum),
     data=BG[BG[,"Condition"]=="Easy",])->EasyMaxLbModel
summary(EasyMaxLbModel)
confint(EasyMaxLbModel)

#Hard condition linear mixed model for pulling force
lmer(MaxPSI_sqrt~TrialNumber+(1|SubjNum),
     data=BG[BG[,"Condition"]=="Hard",])->HardMaxLbModel
summary(HardMaxLbModel)
confint(HardMaxLbModel)
```


######################################################
#   Section 3 Help Seeking Analyses   #
###################################################### 


Figure 2. Frequency of help seeking behaviors,  
across conditions and trials(right, n = 96 infants).  

```{r helping-seeking-plot, echo = FALSE}
#visualize
BG_Trial1 %>% ggplot(aes(x=Condition,y= HelpSeekingNum_exp_avg))+geom_boxplot(alpha=.6,outlier.shape=NA)+
  geom_jitter(alpha=.2,width=.1)+ylab("mean requests for help")+
  theme(axis.text.x = element_text(size = 24, angle = 45, hjust = 1, vjust = 1),
        axis.title.x = element_text(size=24),axis.text.y = element_text(size=24),
        axis.title.y=element_text(size=24))+ theme(legend.position = "none") +xlab("")+theme_bw()+
  theme(legend.position="None")+theme(strip.text = element_text(size = 15))+
  theme(axis.text.x =element_text(size = 15))+theme(axis.text.y =element_text(size = 15))+
  theme(axis.title.y =element_text(size = 15))+theme(axis.title.x =element_text(size = 15))+
  scale_fill_manual(values=cbbPalette)
```

```{r helping-seeking-table,  results = 'asis', echo = FALSE}
#descriptive stats help seeking
MeanHelpSeeking  <- BG_Trial1%>%
  group_by(Condition)%>%
  filter(!is.na(HelpSeekingNum_exp_avg)) %>%
  summarise(n=n(),
            mean_numreachespoints= mean(HelpSeekingNum_exp_avg,na.rm=TRUE),
            sd = sd(HelpSeekingNum_exp_avg,na.rm=TRUE),
            se = sd/sqrt(n))
 knitr::kable(MeanHelpSeeking)
```

Help seeking generalized linear mixed effect model
```{r helping-seeking-analysis-part1}
#analyze help seeking behavior to find no condition*trial interaction
summary(glmer(HelpSeekingNum_exp~TrialNumber*Condition+(1|SubjNum),
              family="poisson",data=BG,
              glmerControl(optimizer="bobyqa",optCtrl = list(maxfun =100000))))
```

```{r helping-seeking-analysis-part2}
#Since trial number did not impact help seeking behaviors, remove this predictor to improve model parsimony and analyze help seeking behaviors collapsed across all three trials, compute CIs, and compare reduced and full models,
#Run help seeking analysis with easy as baseline
lm(HelpSeekingNum_exp_avg~Condition,data=BG_Trial1)->HelpSeekingModel
summary(HelpSeekingModel)
confint(HelpSeekingModel)
lm(HelpSeekingNum_exp_avg~1,data=BG_Trial1)->mnull
AIC(mnull)-AIC(HelpSeekingModel)
anova(mnull,HelpSeekingModel,test= "Chisq")

```

Help seeking in test vs recovery
```{r helping-seeking-analysis-part3}

#rate of help seeking (as opposed to number of help requests) was used in order to compare data across test and recovery trials.

#paired sample t-test, help seeking in test vs recovery, easy cond: 
subset(BG_Trial1, Condition == "Easy") -> RecoveryAnalyses_Easy

t.test(RecoveryAnalyses_Easy$HelpSeekingRate_Recovery, 
       RecoveryAnalyses_Easy$HelpSeekingRate_exp_avg,paired=TRUE)

cohensD(RecoveryAnalyses_Easy$HelpSeekingRate_Recovery, 
        RecoveryAnalyses_Easy$HelpSeekingRate_exp_avg,method="paired")

#paired sample t-test, help seeking in test vs recovery, hard cond: 
subset(BG_Trial1, Condition == "Hard") -> RecoveryAnalyses_Hard
t.test(RecoveryAnalyses_Hard$HelpSeekingRate_Recovery, 
       RecoveryAnalyses_Hard$HelpSeekingRate_exp_avg,paired=TRUE)

cohensD(RecoveryAnalyses_Hard$HelpSeekingRate_Recovery, 
        RecoveryAnalyses_Hard$HelpSeekingRate_exp_avg,method="paired")

#paired sample t-test, help seeking in test vs recovery, impossible cond: 
subset(BG_Trial1, Condition == "Impossible") -> RecoveryAnalyses_Impossible

t.test(RecoveryAnalyses_Impossible$HelpSeekingRate_Recovery, 
       RecoveryAnalyses_Impossible$HelpSeekingRate_exp_avg,paired=TRUE)

cohensD(RecoveryAnalyses_Impossible$HelpSeekingRate_Recovery, 
        RecoveryAnalyses_Impossible$HelpSeekingRate_exp_avg,method="paired")
```


######################################################
#   Section 4: Affect Analyses   #
###################################################### 

## Section 4.1 Negative Affect Analyses
Figure 3. Infants’ behavior across conditions and trials,  
negative affect (center, n = 218 trials).  

```{r affect-negative-plot, , echo = FALSE}
#visualize negative affect in box plot
ggplot(BG, mapping = aes(x = TrialNumber_AsFactor, y = TotalNegFrames/NumAffectFrames,
                         fill=TrialNumber_AsFactor)) +
  geom_boxplot(alpha=.6,outlier.shape=NA)+geom_jitter(alpha=.2,width=.1)+
  scale_fill_manual(values=cbbPalette)+ylab("Proportion Negative Affect")+
  xlab("Trial Number")+facet_wrap(~Condition) +theme_bw()+ theme(legend.position="None")+
  theme(strip.text = element_text(size = 15))+theme(axis.text.x =element_text(size = 15))+
  theme(axis.text.y =element_text(size = 15))+theme(axis.title.y =element_text(size = 15))+
  theme(axis.title.x =element_text(size = 15))
```


```{r affect-negative-table,  results = 'asis', , echo = FALSE}
#descriptive stats neg affect
MeanNegAffect  <- BG%>%
  group_by(Condition,TrialNumber)%>%
  filter(!is.na(NumAffectFrames)) %>%
  summarise(n=n(),
            mean_negaffect= mean(TotalNegFrames/NumAffectFrames,na.rm=TRUE),
            sd = sd(TotalNegFrames/NumAffectFrames,na.rm=TRUE),
            se = sd/sqrt(n))
 knitr::kable(MeanNegAffect)
```


```{r affect-negative-analysis_part1}
#analyze negative affect, compute CIs, and compare models, with hard as baseline
glmer(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~Condition_HardBase*TrialNumber+
        (1|SubjNum),data=BG,family="binomial",
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->NegAffectModel

summary(NegAffectModel)

confint(NegAffectModel)

glmer(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~(1|SubjNum),data=BG,family="binomial",
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->m0

anova(m0,NegAffectModel)

#analyze negative affect, compute CIs, and compare models, with easy as baseline
glmer(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~Condition*TrialNumber+
        (1|SubjNum),data=BG,family="binomial",
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->NegAffectModel

summary(NegAffectModel)

confint(NegAffectModel)

glmer(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~(1|SubjNum),
      data=BG,family="binomial",glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->m0

anova(m0,NegAffectModel)
```

```{r affect-negative-analysis_part2}
#test for simple ME of trial number within each condition on negative affect & compute CIs, with hard as baseline

#Impossible condition
glmer(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~TrialNumber+(1|SubjNum),
      family="binomial",data=BG[BG[,"Condition_HardBase"]=="Impossible",],
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->ImpossibleNegAffectModel
summary(ImpossibleNegAffectModel)
confint(ImpossibleNegAffectModel)

#Hard condition
glmer(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~TrialNumber+(1|SubjNum),
      family="binomial",data=BG[BG[,"Condition_HardBase"]=="Hard",],
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->HardNegAffectModel
summary(HardNegAffectModel)
confint(HardNegAffectModel)

#Easy condition
glmer(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~TrialNumber+(1|SubjNum),
      family="binomial",data=BG[BG[,"Condition_HardBase"]=="Easy",],
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->EasyNegAffectModel
summary(EasyNegAffectModel)
confint(EasyNegAffectModel)

```

## Section 4.2 Positive Affect Analyses
Figure 3. Infants’ behavior across conditions and trials,  
frequency of positive affect (left, n = 218 trials)  

```{r affect-positive-plot, echo = FALSE}
#data viz in boxplot
ggplot(BG, mapping = aes(x = TrialNumber_AsFactor, y = TotalPosFrames/NumAffectFrames,
                         fill=TrialNumber_AsFactor)) +
  geom_boxplot(alpha=.6,outlier.shape=NA)+geom_jitter(alpha=.2,width=.1)+
  scale_fill_manual(values=cbbPalette)+ylab("Proportion Positive Affect")+
  xlab("Trial Number")+facet_wrap(~Condition) +theme_bw()+ theme(legend.position="None")+
  theme(strip.text = element_text(size = 15))+theme(axis.text.x =element_text(size = 15))+
  theme(axis.text.y =element_text(size = 15))+theme(axis.title.y =element_text(size = 15))+
  theme(axis.title.x =element_text(size = 15))
```


```{r affect-positive-table,  results = 'asis', echo = FALSE}
#descriptive stats pos affect
MeanPosAffect  <- BG%>%
  group_by(Condition,TrialNumber)%>%
  filter(!is.na(NumAffectFrames)) %>%
  summarise(n=n(),
            mean_posaffect= mean(TotalPosFrames/NumAffectFrames,na.rm=TRUE),
            sd = sd(TotalPosFrames/NumAffectFrames,na.rm=TRUE),
            se = sd/sqrt(n))
knitr::kable(MeanPosAffect)
```


```{r affect-positive-analysis-part1}
#analyze positive affect, generate CIs, and run model comparisons, with hard as baseline
glmer(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~Condition_HardBase*TrialNumber+
        (1|SubjNum),data=BG,family="binomial",
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->pos_affect_model

summary(pos_affect_model)

confint(pos_affect_model)

glmer(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~(1|SubjNum),
      data=BG,family="binomial",glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->m0

anova(m0,pos_affect_model)

#analyze positive affect, generate CIs, and run model comparisons, with easy as baseline
glmer(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~Condition*TrialNumber+
        (1|SubjNum),data=BG,family="binomial",
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->pos_affect_model

summary(pos_affect_model)

confint(pos_affect_model)

glmer(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~(1|SubjNum),
      data=BG,family="binomial",glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->m0

anova(m0,pos_affect_model)

```

```{r affect-postive-analysis-part2}
#analyze simple ME of trial num on positive affect and compute CIs

#impossible
glmer(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~TrialNumber+(1|SubjNum),
      family="binomial",data=BG[BG[,"Condition"]=="Impossible",],
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->ImpossiblePosAffectModel
summary(ImpossiblePosAffectModel)
confint(ImpossiblePosAffectModel)

#Hard
glmer(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~TrialNumber+(1|SubjNum),
      family="binomial",data=BG[BG[,"Condition"]=="Hard",],
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->HardPosAffectModel
summary(HardPosAffectModel)
confint(HardPosAffectModel)

#Easy
glmer(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~TrialNumber+(1|SubjNum),
      family="binomial",data=BG[BG[,"Condition"]=="Easy",],
      glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))->EasyPosAffectModel
summary(EasyPosAffectModel)
confint(EasyPosAffectModel)
```


######################################################
#   Section 5 Recovery Trial Support Analyses   #
###################################################### 

Figure 3. Infants’ behavior across conditions and trials, number of hints  
provided during the recovery trial (right, n = 94 infants).  

```{r recovery-plot, echo = FALSE}
#data viz in boxplot
ggplot(BG_Trial1, mapping = aes(x = Condition, y = NumHints_Recovery )) +
  geom_boxplot(alpha=.6,outlier.shape=NA)+geom_jitter(alpha=.2,width=.1)+
  scale_fill_manual(values=cbbPalette)+ylab("Average Support Provided")+
  xlab("Condition")+theme_bw()+ theme(legend.position="None")+
  theme(axis.text.x =element_text(size = 15))+theme(axis.text.y =element_text(size = 15))+
  theme(axis.title.y =element_text(size = 15))+theme(axis.title.x =element_text(size = 15))
```


```{r recovery-table, results = 'asis', echo = FALSE}
#descriptive stats recovery
MeanHints  <- BG_Trial1%>%
  group_by(Condition)%>%
  filter(!is.na(NumHints_Recovery)) %>%
  summarise(n=n(),
            mean_numhints= mean(NumHints_Recovery,na.rm=TRUE),
            sd = sd(NumHints_Recovery,na.rm=TRUE),
            se = sd/sqrt(n))
 knitr::kable(MeanHints)
```


```{r recovery-analysis}

#analyze hint data, compute CIs, and run model comparisons w/ hard as baseline condition
BG_Trial1$Condition <- factor(BG_Trial1$Condition, levels=c("Hard","Impossible", "Easy"))

glm(NumHints_Recovery~Condition,data=BG_Trial1,family="poisson")->HintModel

summary(HintModel)

confint(HintModel)

glm(NumHints_Recovery~TrialNumber,data=BG_Trial1,family="poisson")->m0

anova(m0,HintModel,test="Chisq")


#analyze hint data, compute CIs, and run model comparisons w/ easy as baseline condition
BG_Trial1$Condition <- factor(BG_Trial1$Condition, levels=c("Easy","Hard", "Impossible"))

glm(NumHints_Recovery~Condition,data=BG_Trial1,family="poisson")->HintModel

summary(HintModel)

confint(HintModel)

glm(NumHints_Recovery~TrialNumber,data=BG_Trial1,family="poisson")->m0

anova(m0,HintModel,test="Chisq")
```



######################################################
#   Section 6 correlations between time trying and help-seeking   #
###################################################### 


```{r correlation between time trying and help-seeking}

#help seeking x time trying

#visualize help seeking x time trying
ggplot(BG,mapping =aes(x=HelpSeekingNum_exp,y=TimeTrying))+geom_point(alpha=.6)+geom_smooth(method="lm",se=F,color="darkgray",alpha=.7)+ylab("Time Trying (s)")+xlab("Number of Help Requests")+geom_jitter(width=.05,alpha=.6)

#correlate help seeking x time trying
cor.test(BG$HelpSeekingNum_exp, BG$TimeTrying)

#help seeking x time trying within conditions

#subset data by condition to examine within condition correlations
subset(BG, Condition == "Easy") -> BG_Easy
subset(BG, Condition == "Hard") -> BG_Hard
subset(BG, Condition == "Impossible") -> BG_Impossible

#run help seeking x time trying correlations
cor.test(BG_Impossible$HelpSeekingNum_exp,BG_Impossible$TimeTrying)
cor.test(BG_Easy$HelpSeekingNum_exp,BG_Easy$TimeTrying)
cor.test(BG_Hard$HelpSeekingNum_exp,BG_Hard$TimeTrying)

#visualize help seeking x time trying broken down by condition
ggplot(BG,mapping =aes(x=HelpSeekingNum_exp,y=TimeTrying))+geom_point(alpha=.6)+geom_smooth(method="lm",se=F,color="darkgray",alpha=.7)+ylab("Time Trying (s)")+xlab("Number of Help Requests")+geom_jitter(width=.05,alpha=.6)+facet_wrap(~Condition)


```

######################################################
#   Section 7 Analyses in supplemental materials   #
###################################################### 

Planned post-hoc contrasts that are only included in the supplemental materials. 
```{r supplement-time-trying}
#time trying post-hoc contrasts

#t-test within conditions
t.test(timetrying_wide_easy$one, timetrying_wide_easy$three,paired=TRUE,
       alternative="greater")
t.test(timetrying_wide_hard$one, timetrying_wide_hard$three,paired=TRUE,
       alternative="greater")
t.test(timetrying_wide_impossible$one, timetrying_wide_impossible$three,
       paired=TRUE,alternative="greater")

cohensD(timetrying_wide_easy$one, timetrying_wide_easy$three,method="paired")
cohensD(timetrying_wide_hard$one, timetrying_wide_hard$three,method="paired")
cohensD(timetrying_wide_impossible$one, timetrying_wide_impossible$three,method="paired")

```


```{r supplement-force-part1}
#force gauge post-hoc contrasts

##subset force data data for planned post hoc comparisons
force_subset <- BG %>% select(SubjNum,TrialNumber,MaxPSI_sqrt,Condition)
force_wide <- spread(data = force_subset, key = TrialNumber, value = MaxPSI_sqrt) 
force_wide<- rename(force_wide, "one" = "1")
force_wide<- rename(force_wide, "two" = "2")
force_wide<- rename(force_wide, "three" = "3")
force_wide_easy <- subset(force_wide, Condition=="Easy")
force_wide_hard <- subset(force_wide, Condition=="Hard")
force_wide_impossible <- subset(force_wide, Condition=="Impossible")

#t-test within conditions
t.test(force_wide_hard$one, force_wide_hard$three,paired=TRUE,alternative="less")

cohensD(force_wide_hard$one, force_wide_hard$three,method="paired")
```


```{r supplement-force-part2}
#contrasts across conditions for PSI within the first trial

#comparing hard vs. easy
BG_NoImpossible<-subset(BG,!Condition == "Impossible")
BG_NoImpossible_TrialOne<-subset(BG_NoImpossible,TrialNumber == "1")
t.test(MaxPSI_sqrt ~ Condition, alternative="greater",data=BG_NoImpossible_TrialOne)

#comparing impossible vs. easy
BG_NoHard<-subset(BG,!Condition == "Hard")
BG_NoHard_TrialOne<-subset(BG_NoHard,TrialNumber == "1")
t.test(MaxPSI_sqrt ~ Condition,alternative="greater", data=BG_NoHard_TrialOne)

#comparing impossible vs. hard
BG_NoEasy<-subset(BG,!Condition == "Easy")
BG_NoEasy_TrialOne<-subset(BG_NoEasy,TrialNumber == "1")
t.test(MaxPSI_sqrt ~ Condition, alternative="greater",data=BG_NoEasy_TrialOne)

```


```{r supplement-force-part3}
#contrasts across conditions for PSI within the final trial

#impossible vs. easy
BG_NoHard<-subset(BG,!Condition == "Hard")
BG_NoHard_TrialThree<-subset(BG_NoHard,TrialNumber == "3")
t.test(MaxPSI_sqrt ~ Condition,alternative="greater", data=BG_NoHard_TrialThree)

#hard vs. easy
BG_NoImpossible<-subset(BG,!Condition == "Impossible")
BG_NoImpossible_TrialThree<-subset(BG_NoImpossible,TrialNumber == "3")
t.test(MaxPSI_sqrt ~ Condition,alternative="greater", data=BG_NoImpossible_TrialThree)

#impossible vs. hard
BG_NoEasy<-subset(BG,!Condition == "Easy")
BG_NoEasy_TrialThree<-subset(BG_NoEasy,TrialNumber == "3")
t.test(MaxPSI_sqrt ~ Condition,alternative="greater", data=BG_NoEasy_TrialThree)
```

```{r supplement-help seeking}
#relevel hard for comparisons

BG_Trial1$Condition_HardBase <- factor(BG_Trial1$Condition_HardBase, levels=c("Hard","Easy", "Impossible")) #Hard is baseline

#analyze help seeking with hard as baseline
lm(HelpSeekingNum_exp_avg~Condition_HardBase,data=BG_Trial1)->HelpSeekingModel
summary(HelpSeekingModel)


```




```{r supplement-affect_negative_part1}
#affect analyses

#test for simple ME of cond for negative affect within first and final trials
#    with easy as baseline
glm(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~Condition,
    family="binomial",data=BG[BG[,"TrialNumber"]=="1",])->NegAffectFirstTrial
summary(NegAffectFirstTrial)
confint(NegAffectFirstTrial)

glm(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~Condition,
    family="binomial",data=BG[BG[,"TrialNumber"]=="3",])->NegAffectFinalTrial
summary(NegAffectFinalTrial)
confint(NegAffectFinalTrial)

#test for simple ME of cond for negative affect within first and final trials
#    with hard as baseline
glm(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~Condition_HardBase,
    family="binomial",data=BG[BG[,"TrialNumber"]=="1",])->NegAffectFirstTrial
summary(NegAffectFirstTrial)
confint(NegAffectFirstTrial)

glm(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~Condition_HardBase,
    family="binomial",data=BG[BG[,"TrialNumber"]=="3",])->NegAffectFinalTrial
summary(NegAffectFinalTrial)
confint(NegAffectFinalTrial)

```


```{r supplement-affect-negative-part2}
#Test for precise difference between affect on trials 1 and 3 within each condition
# for negative affect 

#Easy condition
glm(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~TrialNumber_AsFactor,family="binomial",
    data=BG[BG[,"Condition"]=="Easy",])->EasyNegAffectModel_FirstVsFinal
summary(EasyNegAffectModel_FirstVsFinal)
confint(EasyNegAffectModel_FirstVsFinal)

#Hard condition
glm(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~TrialNumber_AsFactor,family="binomial",
    data=BG[BG[,"Condition"]=="Hard",])->HardNegAffectModel_FirstVsFinal
summary(HardNegAffectModel_FirstVsFinal)
confint(HardNegAffectModel_FirstVsFinal)

#Impossible condition
glm(cbind(TotalNegFrames,NumAffectFrames-TotalNegFrames)~TrialNumber_AsFactor,family="binomial",
    data=BG[BG[,"Condition"]=="Impossible",])->ImpossibleNegAffectModel_FirstVsFinal
summary(ImpossibleNegAffectModel_FirstVsFinal)
confint(ImpossibleNegAffectModel_FirstVsFinal)

```


```{r supplement-affect-positive-part1}
#test for simple ME of cond for Positive affect within first and final trials
#    with easy as baseline
glm(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~Condition,
    family="binomial",data=BG[BG[,"TrialNumber"]=="1",])->PosAffectFirstTrial
summary(PosAffectFirstTrial)
confint(PosAffectFirstTrial)

glm(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~Condition,
    family="binomial",data=BG[BG[,"TrialNumber"]=="3",])->PosAffectFinalTrial
summary(PosAffectFinalTrial)
confint(PosAffectFinalTrial)

#test for simple ME of cond for Positive affect within first and final trials
#    with hard as baseline
#first trial
glm(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~Condition_HardBase,
    family="binomial", data=BG[BG[,"TrialNumber"]=="1",])->PosAffectFirstTrial
summary(PosAffectFirstTrial)
confint(PosAffectFirstTrial)

#final trial
glm(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~Condition_HardBase,
    family="binomial",data=BG[BG[,"TrialNumber"]=="3",])->PosAffectFinalTrial
summary(PosAffectFinalTrial)
confint(PosAffectFinalTrial)

```


```{r supplement-affect-positive-part2}
#Test for precise differences between affect on trials 1 and 3 within each condition
# for positive affect 

#Easy
glm(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~TrialNumber_AsFactor,
    family="binomial",data=BG[BG[,"Condition"]=="Easy",])->EasyPosAffectModel_FirstVsFinal
summary(EasyPosAffectModel_FirstVsFinal)
confint(EasyPosAffectModel_FirstVsFinal)

#Hard
glm(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~TrialNumber_AsFactor,
    family="binomial",data=BG[BG[,"Condition"]=="Hard",])->HardPosAffectModel_FirstVsFinal
summary(HardPosAffectModel_FirstVsFinal)
confint(HardPosAffectModel_FirstVsFinal)

#Impossible
glm(cbind(TotalPosFrames,NumAffectFrames-TotalPosFrames)~TrialNumber_AsFactor,family="binomial",
    data=BG[BG[,"Condition"]=="Impossible",])->ImpossiblePosAffectModel_FirstVsFinal
summary(ImpossiblePosAffectModel_FirstVsFinal)
confint(ImpossiblePosAffectModel_FirstVsFinal)
```

